Hire Ed: Job Market Dynamics for Tenure-Track Faculty Positions in Archaeology

### 2025-02-04 analysis/paper/article.qmd
add peer review link to draft Zenodo repo (manually uploaded from GitHub)

The entire R code [@rlanguage] and data files used for all the analyses and visualizations contained in this paper are openly available at https://doi.org/xxx/xx to enable re-use of materials and improve reproducibility and transparency [@Marwick2017]. All of the figures, tables, and statistical test results presented here can be independently reproduced with the code and data in this repository. The code is released under the MIT license, the data as CC-0, and the figures as CC-BY, to enable maximum re-use.

@@

The data that support the findings of this study are openly available in Zenodo at http://doi.org/xxx/xxx.

@@

Our supplementary materials are available at http://doi.org/xxx/xxx.

>>>>

The entire R code [@rlanguage] and data files used for all the analyses and visualizations contained in this paper are openly available at https://doi.org/xxx/xx [ for peer reviewers the link is https://zenodo.org/records/14798942?preview=1&token=eyJhbGciOiJIUzUxMiJ9.eyJpZCI6ImMyYWE2MDc3LTMxMzAtNDM1Yi1hYTJkLWMyMGMyNWVhOWMyYiIsImRhdGEiOnt9LCJyYW5kb20iOiJiMjkyMTAyN2UwNzEwNWQ2OWIyZmQ4OTkwMjU0MzY1YyJ9.slnC1BbNgZkiJjrRqmKFK9a1bpI-e9VBbjcU7L5OEeYFs3whcL3POsfVj7phDnoaB5A_6mP9wpGirEaT9Dtvug ] to enable re-use of materials and improve reproducibility and transparency [@Marwick2017]. All of the figures, tables, and statistical test results presented here can be independently reproduced with the code and data in this repository. The code is released under the MIT license, the data as CC-0, and the figures as CC-BY, to enable maximum re-use.

@@

The data that support the findings of this study are openly available in Zenodo at http://doi.org/xxx/xxx. For peer review the link is: https://zenodo.org/records/14798942?preview=1&token=eyJhbGciOiJIUzUxMiJ9.eyJpZCI6ImMyYWE2MDc3LTMxMzAtNDM1Yi1hYTJkLWMyMGMyNWVhOWMyYiIsImRhdGEiOnt9LCJyYW5kb20iOiJiMjkyMTAyN2UwNzEwNWQ2OWIyZmQ4OTkwMjU0MzY1YyJ9.slnC1BbNgZkiJjrRqmKFK9a1bpI-e9VBbjcU7L5OEeYFs3whcL3POsfVj7phDnoaB5A_6mP9wpGirEaT9Dtvug

@@

Our supplementary materials are available at http://doi.org/xxx/xxx.  For peer review the link is: https://zenodo.org/records/14798942?preview=1&token=eyJhbGciOiJIUzUxMiJ9.eyJpZCI6ImMyYWE2MDc3LTMxMzAtNDM1Yi1hYTJkLWMyMGMyNWVhOWMyYiIsImRhdGEiOnt9LCJyYW5kb20iOiJiMjkyMTAyN2UwNzEwNWQ2OWIyZmQ4OTkwMjU0MzY1YyJ9.slnC1BbNgZkiJjrRqmKFK9a1bpI-e9VBbjcU7L5OEeYFs3whcL3POsfVj7phDnoaB5A_6mP9wpGirEaT9Dtvug
